Draft Final Project

### 2020-05-01 Draft-Report.Rmd
Complex mod

```{r results = "hide", echo=FALSE, warning=FALSE}
Finaldata<-read_csv("time_series_final_Data.csv")

@@

## Model(s)

## Model Evaluation

>>>>

```{r results = "hide", echo=FALSE, warning=FALSE}

Finaldata<-read_csv("time_series_final_Data.csv")

@@

## 3.1 Model(s)

###Complex Model

*White, StateColor, Day, Positive Cases, State

```{r results = "hide", include = FALSE}
View(Finaldata)
set.seed(454)
Finaldata<-
  Finaldata%>%
  mutate(Day=as.numeric(Day))

complexmod <- stan_glmer(
  ChinaVirusInterest ~ Day + StateColor + percent_white + positive + (Day | State), 
  data = Finaldata, family = gaussian, chains = 4, iter = 5000*2
)
```

```{r}
head(data.frame(summary(complexmod)),-2)
```

## 3.2 Model Evaluation

###Complex Model

```{r}
# Trace plots
mcmc_trace(complexmod)

# Density plots
mcmc_dens_overlay(complexmod)
```

```{r}
pp_check(complexmod, nreps = 50)
```

```{r}
# Store the chains
model_complex_df <- as.array(complexmod) %>%
  melt %>%
  pivot_wider(names_from = parameters, values_from = value)

# Wrangle the chains
model_complex_df <- model_complex_df %>%
  mutate(sigma_sq_w = `sigma`, sigma_sq_b = `Sigma[State:(Intercept),(Intercept)]`) %>%
  mutate(correlation = (sigma_sq_b/(sigma_sq_b+sigma_sq_w)))

#Correlation Plot
ggplot(model_complex_df, aes(x = correlation)) +
  geom_density(alpha = 0.5)
```

## 3.3 Model Predictions

###Complex Model

```{r}
set.seed(454)

new_data <- data.frame(Day = 7 , State = "FL",percent_white = 0.5, positive_rate = 0.11) 
new_pred <- posterior_predict(
  complexmodel,
  newdata = new_data)

my_pred <- data.frame(y_new = new_pred[-1])

ggplot(my_pred, aes(x=y_new))+geom_density()

summary(my_pred)
```
